\section{Modelo de datos relacional}

  \paragraph{}Las tablas obtenidas después de la normalización son las
  siguientes:

  \begin{itemize}
   \item Tabla Centros.
   \item Tabla AdministradoresCentro.
   \item Tabla Titulaciones.
   \item Tabla Asignaturas.
   \item Tabla AsignaturasCursoAcadémico.
   \item Tabla Departamentos.
   \item Tabla Asesores.
   \item Tabla AsesoresCursoAcadémico.
   \item Tabla PlantillasEntrevistaAsesor.
   \item Tabla PreguntasAsesores.
   \item Tabla Alumnos.
   \item Tabla AlumnosCursoAcadémico.
   \item Tabla CalificacionesAlumnoAsignaturaCA.
   \item Tabla PlantillasEntrevistaOficial.
   \item Tabla PreguntasOficiales.
   \item Tabla Reuniones.
   \item Tabla Centro\_AdministradoresCentro.
   \item Tabla Reunión\_PreguntasAsesor.
   \item Tabla Reunión\_PreguntasOficiales.
  \end{itemize}

\input{10.Disenyo_Datos/10.2.Modelo_Datos_Relacional/Tablas/tCentro.tex}
\input{10.Disenyo_Datos/10.2.Modelo_Datos_Relacional/Tablas/tAdmCentro.tex}
\input{10.Disenyo_Datos/10.2.Modelo_Datos_Relacional/Tablas/tTitulacion.tex}
\input{10.Disenyo_Datos/10.2.Modelo_Datos_Relacional/Tablas/tAsignatura.tex}
\input{10.Disenyo_Datos/10.2.Modelo_Datos_Relacional/Tablas/tACA.tex}
\input{10.Disenyo_Datos/10.2.Modelo_Datos_Relacional/Tablas/tDepartamento.tex}
\input{10.Disenyo_Datos/10.2.Modelo_Datos_Relacional/Tablas/tAsesor.tex}
\input{10.Disenyo_Datos/10.2.Modelo_Datos_Relacional/Tablas/tAsesorCA.tex}
\input{10.Disenyo_Datos/10.2.Modelo_Datos_Relacional/Tablas/tPlantEntAse.tex}
\input{10.Disenyo_Datos/10.2.Modelo_Datos_Relacional/Tablas/tPregAse.tex}
\input{10.Disenyo_Datos/10.2.Modelo_Datos_Relacional/Tablas/tAlumno.tex}
\input{10.Disenyo_Datos/10.2.Modelo_Datos_Relacional/Tablas/tAlCA.tex}
\input{10.Disenyo_Datos/10.2.Modelo_Datos_Relacional/Tablas/tCalAlACA.tex}
\input{10.Disenyo_Datos/10.2.Modelo_Datos_Relacional/Tablas/tPlantEntOfi.tex}
\input{10.Disenyo_Datos/10.2.Modelo_Datos_Relacional/Tablas/tPregOfi.tex}
\input{10.Disenyo_Datos/10.2.Modelo_Datos_Relacional/Tablas/tReunion.tex}
\input{10.Disenyo_Datos/10.2.Modelo_Datos_Relacional/Tablas/tCentro_AdmCentro.tex}
\input{10.Disenyo_Datos/10.2.Modelo_Datos_Relacional/Tablas/tReunion_PregAse.tex}
\input{10.Disenyo_Datos/10.2.Modelo_Datos_Relacional/Tablas/tReunion_PregOfi.tex}
